\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-01-19 paper/subdocuments/data_and_methods.Rnw
playig with zeros

<<zero_descriptives>>=
library(ggplot2)
df$zeros <- df$null_norm/df$cpop # i only use normal cases here
ggplot(df[df$steuerperiode>=1995,], aes(x=steuerperiode,y=zeros))+geom_line()+facet_wrap(~kanton)
@

@@

@@

A negative coefficient (e.g. Geneva) means the more zeros there the are the smaller the gini measure was compared to other tax periods within that canton (remember this is a fixed-effects model). This is less obvious than the Schwyz case and our reading is: more zeros mask inequality that arises from the bottom.

>>>>

<<zero_descriptives>>=
library(ggplot2)
df$zeros <- df$null_norm/df$cpop # i only use normal cases here
ggplot(df[df$steuerperiode>=1995,], aes(x=steuerperiode,y=zeros))+geom_line()+facet_wrap(~kanton)
ggplot(df[df$steuerperiode>=1995,], aes(x=steuerperiode,y=zeros))+geom_line()+facet_wrap(~kanton)+geom_line(aes(y=G),color="blue")
@

@@

<<echo=FALSE>>=
# checking the impact of zeros on an artificial distribution
# generate a few differently scewed distributions and introduce zeros.
x02 <- rgamma(1000,shape=0.2,scale=5)
x05 <- rgamma(1000,shape=0.5,scale=2)
x1 <- rgamma(1000,shape=1,scale=1/1)
x2 <- rgamma(1000,shape=2,scale=1/2)
x3 <- rgamma(1000,shape=3,scale=1/3)
x4 <- rgamma(1000,shape=4,scale=1/4)
x1 <- x1[order(x1)]
x2 <- x2[order(x2)]
x3 <- x3[order(x3)]
x4 <- x4[order(x4)]
# delete the lowest 20%
x02_20 <- x02
x02_20[1:200] <- NA
x05_20 <- x05
x05_20[1:200] <- NA
x1_20 <- x1
x1_20[1:200] <- NA
x2_20 <- x2
x2_20[1:200] <- NA
x3_20 <- x3
x3_20[1:200] <- NA
x4_20 <- x4
x4_20[1:200] <- NA

gini(x02)-gini(na.omit(x02_20))

gini(x05)-gini(na.omit(x05_20))

gini(x1)-gini(na.omit(x1_20))

gini(x2)-gini(na.omit(x2_20))

gini(x3)-gini(na.omit(x3_20))

gini(x4)-gini(na.omit(x4_20))
# gini inceases
@

@@

A negative coefficient (e.g. Geneva) means the more zeros there are the smaller the gini measure was compared to other tax periods within that canton (remember this is a fixed-effects model). This is less obvious than the Schwyz case and our reading is: more zeros mask inequality that arises from the bottom.

\subsubsection{Descriptives - where do we put this?}
nice grapics for taxable income, reines einkommen and income after taxes here...
